An Analysis of Parallel Rendering Systems

### 2006-09-19 WhitePapers/ParallelRenderingSystems/paper.tex
Add project description document to web site, rewrite overview page, other minor updates to the web site
Add overview presentation, tweak layering figure in overview presentation and project white paper

% paragraph spacing -- should be rubber length
%\setlength{\parskip}{1.5ex plus 0.5ex minus 0.5ex}
% paragraph indention for the first line
%\setlength{\parindent}{0em}

@@

We advocate the need for a generic, open parallel rendering framework to
build scalable graphics software. The inherent limitations of transparent
multi-pipe software are justified, and a full software stack for
graphics clusters is outlined.
}
\vfill
\begin{tabularx}{.85\columnwidth}{|l|l|X|}
\hline
\bf Version & \bf Date & \bf Changes \\
\hline
0.5         & May 19, 2006   & Initial Version\\
\hline
\end{tabularx}
\clearpage
\pagenumbering{arabic}

>>>>

% paragraph spacing -- should be rubber length
%\setlength{\parskip}{\baselineskip}
% paragraph indention for the first line
%\setlength{\parindent}{0em}

@@

We advocate the need for a generic, open parallel rendering framework to
build scalable graphics software. The inherent limitations of transparent
multi-pipe software are justified, and a full software stack for
graphics clusters is outlined.
}
\vfill
{\center\begin{tabularx}{.88\textwidth}{|l|l|X|}
\hline
\bf Version & \bf Date & \bf Changes \\
\hline
0.5.2       & September 19, 2006   & Tweaked Figure~\ref{FIG_parallel}\\
0.5.1       & July 5, 2006         & Added link to latest version\\
0.5         & May 19, 2006         & Initial Version\\
\hline
\multicolumn{3}{c}{\footnotesize Latest version at 
  \htmladdnormallink{http://www.equalizergraphics.com/documents/ParallelRenderingSystems.pdf}
  {http://www.equalizergraphics.com/documents/ParallelRenderingSystems.pdf}}\\
\end{tabularx}}
\clearpage
\pagenumbering{arabic}
